---
title: "How to run a global subnational model with a spatial component"
author: "Hannah Comiskey"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

    - This vignette explains how to estimate and plot model estimates at a subnational level for countries participating in the Family Planning 2030 (FP2030). 
    - We refer to this kind of model run as a 'global' model run as it involves multiple countries from across the world. 
    - In contrast, when we are only using the data for a single country, we call this a 'local' model run. 
    - A vignette for how to run subnational models at the local level can be found in the /vignette folder under 'how_to_run_subnational_local_models.Rmd'.


## Load your library

```{r, include=TRUE, message=FALSE}
library(mcmsupplylocal)
library(dplyr)
```

## Get your data
This function 'get_subnational_data' retrieves the raw family planning subnational source data, applies some basic cleaning and removes observations with samples sizes of less than 5. 

The parameters of this function are: 

* local: Default is FALSE. This indicates whether or not you are running a local (single country) or global (multicountry) model. 
* mycountry: Default is NULL. When local=TRUE, this parameter indicates the name of the country, as a string, whose data you wish to use in your local model run. A list of country names can be found in the /vignette folder under 'country_names.Rmd'. 

```{r}
raw_subnatdata <- mcmsupplylocal::get_subnational_data(local=FALSE, mycountry=NULL) %>%
  dplyr::arrange(Country, Region, Method, average_year)

dplyr::glimpse(raw_subnatdata)
```

## Get the JAGS model inputs and the cleaned data
```{r}
pkg_data <- mcmsupplylocal::get_subnational_modelinputs(fp2030=TRUE, local=FALSE,
                                                          spatial=FALSE, mycountry=NULL,
                                                          startyear=1990, endyear=2028.5,
                                                          nsegments=12, raw_subnatdata)

dplyr::glimpse(pkg_data$data)

```

## Set up your JAGS model

1. Get your global correlations
```{r}
load("data/estimated_global_subnational_correlations.rda")

estimated_rho_matrix <- estimated_global_subnational_correlations %>%
  dplyr::select(row, column, public_cor, private_cor)

head(estimated_rho_matrix)

my_SE_rho_matrix <- estimated_rho_matrix %>%
  dplyr::select(public_cor, private_cor)
```

2. Create your JAGS data list
```{r}
jags_data <- list(y = pkg_data$data[,c("Public", "Commercial_medical")], 
                  se_prop = pkg_data$data[,c("Public.SE", "Commercial_medical.SE")],
                  rho = my_SE_rho_matrix, 
                  kstar = pkg_data$Kstar,
                  B.ik = pkg_data$B.ik, 
                  n_years = pkg_data$n_all_years,
                  n_obs = pkg_data$n_obs,
                  K = pkg_data$K,
                  H = pkg_data$H,
                  C_count = pkg_data$C_count,
                  P_count = pkg_data$P_count,
                  R_count = pkg_data$R_count,
                  M_count = pkg_data$M_count,
                  matchsubnat = pkg_data$matchsubnat,
                  matchcountry = pkg_data$matchcountry,
                  matchregion = pkg_data$matchsuperregion,
                  matchmethod = pkg_data$matchmethod,
                  matchyears = pkg_data$matchyears
)

```

3. Set your parameters to monitor
```{r}
jags_pars <- c("alpha_pms", 
               "alpha_cms",
               "tau_alpha",
               "beta.k",
               "sigma_delta",
               "delta.k")
```

4. Run JAGS model
```{r, eval=FALSE}
mod_global <- run_subnational_jags_model(jagsdata = jags_data, jagsparams = jags_pars, 
                                         local=FALSE, spatial=FALSE, main_path = "results/global_nonspatial/",
                                       n_iter = 80000, n_burnin = 10000, n_thin = 35, mycountry=NULL)

```

5. Get posterior point estimates
```{r, eval=FALSE}
get_P_point_estimates(main_path = "results/global_nonspatial/", pkg_data, local=FALSE, spatial=FALSE, mycountry=NULL)
```


6. Plot posterior point estimates
```{r, eval=FALSE}
plot_point_estimates(main_path = "results/global_nonspatial/", pkg_data = pkg_data, vis_path = "visualisations/global_nonspatial/", local=FALSE, mycountry=NULL)
```

7. Ta-da! We can review the model plots by navigating to the pathway labelled as 'vis_path' from the 'plot_point_estimates' function above.
```{r}
knitr::include_graphics("Ghana_Western_p.pdf", error=FALSE)
```
